
\section*{Brainstorm}
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
	\path[mindmap,
	every node/.style=concept,
	concept color=black,
	scale=0.5,
	text=white,
	text width=2cm,
	grow cyclic,
	level 1/.append style={level distance=8.5cm,sibling angle=70},
	level 2/.append style={level distance=6cm,sibling angle=45}]
	node[concept] {Simple sketch to virtual world}
	[clockwise from=-20]
	child[concept color=green!50!black] {
		node[concept] {Building}
		[clockwise from=-20]
		child { node[concept] {Over construction} }
		child { node[concept] {Overuse of materials} }
	}  
	child[concept color=black!20!blue] {
		node[concept] {Architecture}
		[clockwise from=-67]
		child { node[concept] {Sketching} }
		child { node[concept] {3D modeling} }
	}
	child[concept color=orange] { node[concept] {Presentation} [clockwise from=-90]
		child { node[concept] {Teachers}}
		child { node[concept] {Students}}
	};
	\end{tikzpicture}
	\captionof{figure}{The outcome of the intitial brainstorm}
	\label{fig:brainstorm}
\end{figure}
\section*{Interview Questions for plant center customers}\label{sec:interviewQuestionsCustomer}
% when and where
% what does location and time mean for the data
List of questions for target group
\begin{itemize}
	\item[-] Have you ever used a garden designer?
	\item[-] What was your experience?
	\item[-] What are you planning to buy?
	\item[-] What are you plan/thoughts for when you buy a new plant?
	\item[-] What do you consider when you buy a new item for your garden?
	\item[-] How often do you make major changes to your garden?
	\item[-] For which reasons did you decide to purchase this item?
	\item[-] What was the latest item you bought that you were not satisfied with?
	\item[-] Do you have a garden?
	\item[-] How did you start the design process?
	\item[-] What tools did you use, if any?
	\item[-] When did you make changes to your garden?
	\item[-] What big changes would you like to make?
	\item[-] Are you retired?
	\item[-] If you had all the time in the world, what would you change about your garden?
	\item[-] Do you enter the garden center with a budget in mind?
	\item[-] Why are you here? \\
\end{itemize}

\paragraph*{Demographic information}
\begin{itemize}
	\item[-] Sex
	\item[-] Age
	\item[-] Job
	\item[-] Marital Status
	\item[-] Level of education
\end{itemize}
>>>>>>> 72abfd2e538e998a19c2e3a7f7f088c3990ffb36

\section*{Interview Questions for experts}\label{sec:interviewQuestionsExperts}

Target group questions:
\begin{itemize}
	\item[-] Which people usually addresses you?
	\item[-] What is the most usual demography?
	\item[-] Do people need designing for all or just parts of their garden?
	\item[-] Who makes the 3D visualization of the garden? Is it something you create internally in the company, or does it come from outside cooperators? 
	\item[-] How does this process function?
	\item[-] Do people take the offer on 3D visualization of their garden?
	\item[-] What about development over time? Does it mean that growth can be followed year by year, or does it concern seasons?
	\item[-] Is it something people make use of? \\
\end{itemize}

Technology questions:
\begin{itemize}
	\item[-] How do you think a Virtual Reality experience in the 3D environment would be received?
	\item[-] If a customer could design their own garden in a gardening center and instantly visualize it in Virtual Reality, do you think it would be a popular choice? \\
\end{itemize}

Design questions:
\begin{itemize}
	\item[-] How large of a garden area do you usually work with?
	\item[-] What plants are trending at the moment?
	\item[-] What is a popular garden style?
\end{itemize}